Exploring Determinants of Child Mortality Globally (2022): The Role of Vaccination, Healthcare Spending, and Nutrition

### 2025-04-14 paper/paper.qmd
Intro

>>>>

Strong lensing occurs when a massive foreground object, such as a galaxy cluster, bends light from a more distant source, producing distinctive arcs or rings in images. Despite their significance for cosmology, these events are extremely rare, making up only a small fraction of astronomical observations. Traditional supervised learning methods require large quantities of labeled data, which is infeasible in this context. The primary challenge, therefore, is to develop a system capable of identifying potential lensing candidates with minimal labeled data.
